Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
revised intro to the CEGIS sec + revised some comments

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalization} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
The first checks safety by unwinding the transition relation to a completeness threshold, 
whereas the second employs abstract acceleration.

@@

When mapping back to the notation used for describing the general architecture of the program synthesizer, 
the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
While the controller precision \todo{are these notations updated?} $\langle I_c,F_c\rangle$ is given and fixed, 
we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS.  For this purpose, we first
provide the synthesiser's general architecture, followed by describing
two approaches that use it to automatically generate safe controllers:
the first one is a baseline approach which relies on a naive explicit
unwinding of the transition relation, whereas the second uses an
abstraction to implicitly evaluate all possible progressions of the
system simultaneously. % on an infinite time horizon.

%% We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
%% We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
%% The first checks safety by unwinding the transition relation to a completeness threshold, 
%% whereas the second employs abstract acceleration.

@@

When mapping back to the notation used for describing the general architecture of the program synthesizer, 
the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
%% While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
%% we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.
